Optimal forward modeling of gravitational fields using tesseroids with adaptive discretization

### 2014-09-02 body.tex
Slight mods to shell tex

We must establish reference values to evaluate the error of the numerical
integration.

The homogeneous spherical shell is a convenient geometry with analytical
solutions for
the gravitational potential, attraction, and gravity gradient tensor \citep{Grombein2013}

@@

\noindent
where $r$ is the radial coordinate of the computation point and
$r_1$ and $r_2$ are radial coordinates
of the bottom and top of the spherical shell, respectively.

@@

Table~\ref{tab:shell} contains the parameters defining the spherical shell.

\begin{table}
    \caption{Parameters of the spherical shell.}
    \label{tab:shell}
    \begin{tabular}{lr}
        $\rho$                    & $2.76\ g.cm^{-3}$ \\
        $\Delta r$                & $1\ km$ \\
        $r_1 = R$                 & $6,378.137\ km$ \\
        $r_2 = r_1 + \Delta r$    & $6,379.137\ km$ \\
    \end{tabular}
\end{table}

>>>>

We must establish reference values
to evaluate the error of the numerical integration.
For this purpose, we have used a homogeneous spherical shell
with its bottom at a sphere with radius $R$ (the mean Earth radius),
thickness $\Delta r$, and density $\rho$.
It is a convenient geometry
with analytical solutions for
the gravitational potential, attraction, and gravity gradient tensor
\citep{Grombein2013}

@@

\noindent
where $r$ is the radial coordinate of the computation point and
$r_1 = R$ and $r_2 = r_1 + \Delta r$ are radial coordinates
of the bottom and top of the spherical shell, respectively.
Table~\ref{tab:shell} summarises the parameters defining the spherical shell.

@@

\begin{table}
    \caption{Parameters of the spherical shell.}
    \label{tab:shell}
    \begin{tabular}{lr}
        $\rho$                    & $2.67\ g.cm^{-3}$ \\
        $\Delta r$                & $1\ km$ \\
        $r_1 = R$                 & $6,378.137\ km$ \\
        $r_2 = r_1 + \Delta r$    & $6,379.137\ km$ \\
    \end{tabular}
\end{table}
